---
output: md_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SPL

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/SPL)](https://CRAN.R-project.org/package=SPL)
<!-- badges: end -->

The SPL package allows to estimate cross random effects model for binary and ordinal responses via pairwise likelihood. When dealing with small-to-moderate data dimensions, it is possible to use standard pairwise likelihood. In case of massive datasets, we suggest using stochastic pairise likelihood.

## Installation

You can install the development version of SPL via

``` r
devtools::install_github("giuseppealfonzetti/SPL")
```

## Example Ordinal


```{r example}
library(SPL)

data(InstEval, package = "lme4")
N <- nrow(InstEval); R <- length(unique(InstEval$s)); C <- length(unique(InstEval$d))
N; R; C;

x <- model.matrix(formula("y ~ studage + lectage + service + dept"), data=InstEval)[, -1]

saFIT <- saPL(
    Y = as.numeric(InstEval$y),
    X = x,
    F1 = InstEval$s,
    F2 = InstEval$d,
    MODEL = "ordprobit",
    VERBOSE = 1
  )
```

```{r plot}
plot_sa_traj(saFIT)
```





